### 2022-04-27 ehoh2/ehoh2.tex
new ehoh2 eval

We \NumberOK{evaluated} \ehohii{} on a selection of proof assistants benchmarks
as well as all higher-order theorems in the TPTP library \cite{gs-17-tptp}
(Sect.~\ref{sec:ehoh2:eval}). We found
that \ehohii{} clearly outperformed Ehoh on all benchmarks. It outperformed all other higher-order provers on the
proof assistant benchmarks; on the TPTP benchmarks it ended up second only 
to the cooperative version of Zipperposition, which employs Ehoh as a
backend. An arguably fairer comparison without the backend puts \ehohii{} in
first place for both benchmark suites.
We also compared the performance of \ehohii{} with E on first-order
%%% @PETAR: I made this slightly sentence shorter and more forceful. Please
%%% check if you agree. --JB
problems and found that little overhead has been introduced by the
extension to higher-order logic.

@@

  \ehohii{} dramatically improves the higher-order reasoning capabilities
  compared to Ehoh. It solves \NumberOK{20\%} more problems on TPTP benchmarks
  and \NumberOK{6\%} more problems on SH benchmarks, where Ehoh was already very
  successful.

@@

  Remarkably, there is a substantial disparity in the set of problems solved by
  \ehohii{} and Zipperposition-coop. The raw data show thats \ehohii{} solves
  \NumberOK{166} SH problems and \NumberOK{21} TPTP problems that Zipperposition-coop
  does not. The lower number of uniquely solved TPTP problems is most likely 
  due to Zipperposition's being heavily optimized on TPTP.

@@

                              & TPTP       & SH        \\
        \midrule
        cvc5                  & 1931       & 2577      \\
        Ehoh                  & 2105       & 2611      \\
        \ehohii{}             & 2523       & {\bf 2766}\\
        Leo-III               & 2282       & 1601      \\
        Satallax              & 2320       & 1719      \\
        Vampire               & 2203       & 2240      \\
        Zipperposition-coop   & {\bf 2583} & 2754      \\
        Zipperposition-uncoop & 2483       & 2181      \\
        \bottomrule
      \end{tabular}}
      \caption{Comparison of higher-order provers}
      \label{fig:all-provers}
    \end{minipage}\hfill\hfill
    \begin{minipage}[ht!]{.30\linewidth}
      \centering
      \def\arraystretch{1.1}%
      \relax{\begin{tabular}{l@{\hskip 1em}@{\hskip 0.5em}c} \toprule
                        & TPTP     \\
        \midrule
        Ehoh FO      & 535      \\
        Ehoh HO      & 538      \\
        \ehohii{} FO & {\bf 539}\\
        \ehohii{} HO & {\bf 539}\\
        \bottomrule
      \end{tabular}}
      \caption{Evaluation of \ehohii{}'s overhead}
      \label{fig:ehoh}
    \end{minipage}\hfill\hfill
  \end{figure}

>>>>

We \NumberOK{evaluated} \ehohii{} on a selection of proof assistants benchmarks
as well as all higher-order theorems in the TPTP library \cite{gs-17-tptp}
(Sect.~\ref{sec:ehoh2:eval}). We found
that \ehohii{} clearly outperformed Ehoh on all benchmarks. It outperformed all other higher-order provers on the
proof assistant benchmarks; on the TPTP benchmarks it ended up second only 
to the cooperative version of Zipperposition, which employs Ehoh as a
backend. An arguably fairer comparison without the backend puts \ehohii{} in
first place for both benchmark suites.
We also compared the performance of \ehohii{} with E on first-order
%%% @PETAR: I made this slightly sentence shorter and more forceful. Please
%%% check if you agree. --JB
problems and found that no overhead has been introduced by the
extension to higher-order logic.

@@

  \ehohii{} dramatically improves the higher-order reasoning capabilities
  compared to Ehoh. It solves \NumberOK{20\%} more problems on TPTP benchmarks
  and \NumberOK{7\%} more problems on SH benchmarks, where Ehoh was already very
  successful.

@@

  Remarkably, there is a substantial disparity in the set of problems solved by
  \ehohii{} and Zipperposition-coop. The raw data show thats \ehohii{} solves
  \NumberOK{181} SH problems and \NumberOK{24} TPTP problems that Zipperposition-coop
  does not. The lower number of uniquely solved TPTP problems is most likely 
  due to Zipperposition's being heavily optimized on TPTP.

@@

                              & TPTP       & SH        \\
        \midrule
        cvc5                  & 1931       & 2577      \\
        Ehoh                  & 2105       & 2611      \\
        \ehohii{}             & 2533       & {\bf 2804}\\
        Leo-III               & 2282       & 1601      \\
        Satallax              & 2320       & 1719      \\
        Vampire               & 2203       & 2240      \\
        Zipperposition-coop   & {\bf 2583} & 2754      \\
        Zipperposition-uncoop & 2483       & 2181      \\
        \bottomrule
      \end{tabular}}
      \caption{Comparison of higher-order provers}
      \label{fig:all-provers}
    \end{minipage}\hfill\hfill
    \begin{minipage}[ht!]{.30\linewidth}
      \centering
      \def\arraystretch{1.1}%
      \relax{\begin{tabular}{l@{\hskip 1em}@{\hskip 0.5em}c} \toprule
                        & TPTP     \\
        \midrule
        Ehoh FO      & 535      \\
        Ehoh HO      & 538      \\
        \ehohii{}  FO & 537      \\
        \ehohii{}  HO & {\bf 541}\\
        \bottomrule
      \end{tabular}}
      \caption{Evaluation of \ehohii{}'s overhead}
      \label{fig:ehoh}
    \end{minipage}\hfill\hfill
  \end{figure}
